Assessing the Reliability of JavaScript Engines by Leveraging Diversity

### 2018-08-01 paper/paper.tex
another pass on results

%\begin{wrapfigure}[10]{r}[0pt]{0.45\textwidth}
\begin{figure}[t]
  \centering
%  \includegraphics[trim=20 350 200
%    0,clip,width=0.35\textwidth]{google-awards-workflow}
  \includegraphics[trim=0 350 0 0,clip,width=0.65\textwidth]{diff-testing-runtimes}
  \caption{\label{fig:workflow}Infrastructure.}
\end{figure}

@@

\begin{table}[t]
  \centering
  \caption{\label{tab:test-suites}Test Suites. The sections of the
    table show, respectively, the TC-39 conformance test suite, suites
    from engines we analyzed, and suites from other engines.}
  \begin{tabular}{ccr}
    \toprule
    Name & Source & \# JS files \\
    \midrule
    TC-39 (Test262) & \cite{ecma262-conformance-suite} & 31,276 \\
    \midrule
    Mozilla & \cite{mozilla} & 2,633 \\
    \veight{} & \cite{v8} & 74 \\
    \jsc{} & \cite{webkit} & 1,031 \\
    \midrule    
    Duktape & \cite{duktape} & 1,195 \\ 
    JerryScript & \cite{jerryscript} & 1,950 \\
    JSI & \cite{jsi} & 98 \\
    Tiny-js & \cite{tinyjs} & 48 \\    
    % Chakra & \cite{chakracore} & 2632 \\
    \midrule
     &  & 38,305 \\
   \bottomrule     
  \end{tabular}
\end{table}

@@

Recall that the goal of our study is to assess reliability of
\js\ engines by leveraging the rich diversity of implementations in
this domain. We report results in three parts. First, we report on the
stability of the engines we analyzed using the EcmaScript standard
conformance test suite Test262~\cite{ecma262-conformance-suite}. The
intuition is that the bugs we discover would have low relevance if the
engines are unstable (\ie{}, too fragile). Second, we report results
obtained with test transplantation. The hypothesis is that test cases
written for one engine may reveal bugs in different engines. The
rationale is that the domain of possible inputs is just too large;
consequently, test suites of a given engine will cover scenarios and
corner cases uncovered by another engine.  Third, we analyzed the
impact of using cross-engine differential testing to find bugs in
\js{} engines. \Fix{hypothesis/rationale}

\subsection{Stability of Engines}

@@

\begin{table}[h]
  \centering
  \caption{\label{tab:test262}Results of Test262.}
  \begin{tabular}{crrrrrrr}
    \toprule
           & 1 & 2 & 3 & 4 & 5 & 6 & 7 \\
    \jsc{} & - & - & - & - & - & - & - \\
    \veight{} & - & - & - & - & - & - & - \\
    \chakra{} & - & - & - & - & - & - & - \\
    \smonkey{} & - & - & - & - & - & - & - \\
    \bottomrule 
  \end{tabular}
\end{table}

\subsection{Test Transplantation}

We expanded these results by looking for tests from different
sources. \Fix{elaborate} Table~\ref{tab:cross-testing} shows
results. To sum, we observed that \Fix{...}

\begin{table}[h]
  \centering
  \caption{\label{tab:cross-testing}Crossed execution of test suites..}
  \begin{tabular}{crrrr}
    \toprule
    test suite/engine & \jsc{} & \veight{} & \chakra{} & \smonkey{} \\
    \midrule
    \jsc{} & - & - & - & -  \\
    \veight{} & - & - & - & -  \\
%    \chakra{} & - & - & - & -  \\
    Mozilla & - & - & - & -  \\
    Duktape & - & - & - & -  \\
    JerryScript & - & - & - & -  \\
    JSI & - & - & - & -  \\
    Tiny-js & - & - & - & -  \\
    \bottomrule 
  \end{tabular}
\end{table}

@@

\begin{table*}[h!]
  \vspace{-3ex}
%  \scriptsize
  \centering
  \caption{List of bug reports issued as result of test transplantation.}
  \label{tab:bugs}
  \begin{tabular}{cccccccc}
    \toprule Issue\#    & Date & Fuzz & Engine  & Status  & \multicolumn{1}{c}{Url}  & Severity & Suite \\
    \midrule    
    1  & 4/18 & \crossmark & JavascriptCore  & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}} & \Fix{x} & JerryScript      \\
   2  & 4/23 & \crossmark & Chakra  & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5033}{\#5033}} & \Fix{x} & Mozilla      \\
   3  & 4/29 & \crossmark & Chakra  & \textbf{Confirmed}   &
    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5065}{\#5065}} & \Fix{x} & Mozilla \\
   \multirow{2}{*}{4}  & \multirow{2}{*}{4/29} &  \multirow{2}{*}{\crossmark} & Chakra & \textbf{Confirmed} &    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5067}{\#5067}} & \multirow{2}{*}{\Fix{x}} & \multirow{2}{*}{Mozilla}\\
                       &  &                       &
    JavascriptCore & New &    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130} } &   & \\
   5 & 5/02 & \crossmark & JavascriptCore & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}} & \Fix{x} & Mozilla \\
   6 & 5/17 & \crossmark & Chakra & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5187}{\#5187}} & \Fix{x} & \jsc{}\\
   7 & 5/21 & \crossmark & Chakra & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5203}{\#5203}} & \Fix{x} & Mozilla\\
   8 & 6/28 & \crossmark & Chakra & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5388}{\#5388}} & \Fix{x} & \jsc{}\\
   9 & 7/10 & \crossmark & Chakra & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5442}{\#5442}} & \Fix{x} & JerryScript\\
  10 & 7/18 & \crossmark & Chakra & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5478}{\#5478}} & \Fix{x} & Mozilla\\
   11 & 7/18 & \crossmark & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187777}{\#187777}} & \Fix{x} & JerryScript\\
   \bottomrule
  \end{tabular}
\end{table*}

@@

In the following, we describe the methodology we used to asses the
impact of cross-engine differential testing in finding bugs on \js{}
engines. Recall that our tool outputs a set of buckets, that each
bucket includes a set of warnings, that each warning is related to one
file, and that a bucket is of ``lo'' or ``hi'' importance, according
to the heuristic we defined. Figure~\ref{fig:distribution} shows the
distribution of number of warnings per bucket. We use the the label
``nofuzz'' to refer to the experiment that analyzed the impact of test
mining as we do not use fuzzing in that experiment and use the names
of the fuzzing tools to refer to the results obtained with those
tools. We inspected each and every bucket for bugs, but observe that
the number of files per bucket is very high in some cases (\eg{},
nofuzz [hi]). As such, it would be impractical to manually inspect all
the files in the bucket. For that reason, we only inspected one file
per bucket. For the cases we found the warning suspicious, we analyzed
the parts of the documentation related to the problem and, if still
suspicious, we looked on the bug tracker of the affected engine for
potential duplicates. If none was reported, we filed a bug report
including the test input that manifested the potential problem and
explaining the reasons we were suspicious. In some cases, we used the
Mozila lithium tool~\cite{lithium} to minimize the test case. For the
cases of false positives, we identified the source of false positive
and moved to the next bucket. Table~\ref{tab:summary-of-results}
summarizes our results. It shows, for each execution mode and category
of bucket (\ie{}, hi or lo), the total number of files involved, the
number of buckets reported by our infrastructure, the number of those
that we classified as bug-revealing, and the number of those that we
filed a bug report. The difference between the last two columns
indicate the number of duplicates, \ie{}, the cases of
already-reported bugs. As expected, the hit ratio for the ``hi'' group
is higher.

\begin{table}[t]
  \centering
  \caption{\label{tab:summary-of-results}Summary of results.}
  \begin{tabular}{ccrrrr}
    \toprule
    \multirow{2}{*}{mode} & \multirow{2}{*}{type} & \multirow{2}{*}{\# files} &  \multicolumn{3}{c}{buckets} \\
    \cline{4-6}    
    & & & \multicolumn{1}{c}{\#} & \multicolumn{1}{c}{\# pos.} &
    \multicolumn{1}{c}{\# pos. filed} \\
    \midrule
    %% \multirow{2}{*}{nofuzz} & lo & \nofuzzFilesLO{} &  \nofuzzLOTotal{} & \Fix{.} & 11 (34) \\
    %% & hi & \nofuzzFilesHI{} & \nofuzzHITotal{} & \Fix{.} & \Fix{108 (-)} \\
    \multirow{2}{*}{\radamsa} & lo & \Fix{.} & \Fix{.} & \Fix{.} & \Fix{.} \\
    & hi & \Fix{.} & \Fix{.} & \Fix{.} & \Fix{.} \\
    \multirow{2}{*}{\quickfuzz} & lo & \Fix{.} & \Fix{.} & \Fix{.} & \Fix{.} \\
                             & hi & \Fix{.} & \Fix{.} & \Fix{.} & \Fix{.} \\    
    \bottomrule     
  \end{tabular}
\end{table}

Table~\ref{tab:false-positives} shows the distribution of false
positives per source. A false positive is a bucket that did not reveal
a bug. We identified five sources of imprecision. The source ``not yet
implemented'' indicates that the engine does not implement some part
of the specification. For example, at the time of writing, Chakra does
not implement various properties from the \CodeIn{Symbol} object. The
source ``invalid input'' indicates that the test violated some part of
the specification. For example, the test indirectly invoked some
function with unexpected arguments\Fix{provide concrete example}. In
all cases that we analyzed, that happened because fuzzing produced an
invalid test input. Note that no false positives of this kind appears
under the column nofuzz. The source ``timeout/ome'' indicates that the
test times out (we used a 3s time budget) or runs out of memory. That
happens because engines implement different set of optimizations. For
example, only \jsc{} implements tail-call optimization to avoid tail
recursion. Consequently, for a certain input, it finishes execution
quickly whereas other engines time out. The source
``implementation-dependent'' is as defined in
Section~\ref{sec:imp-dep-behavior}.\Fix{provide concrete example} The
source ``future feature'' corresponds to the case where some feature
will be part of the spec in the future but implementing it is
facultative.\Fix{provide concrete example}

@@

\Igor{
  Neste experimento, obtemos \nofuzzAll{} buckets distintos, a proporcao \'e de 
  \nofuzzHITotal{} HI e apenas \nofuzzLOTotal{} LO. Como descrito anteriormente,
  n\'os analisamos e discutimos se estas discrepancias reportadas pela ferramenta sao 
  casos de bugs reais ou casos de falso positivos.
  Nesta analise, nos observamos que cerca de \Fix{63} buckets sao duplicados, ou seja,
  estes warnings foram reportados anteriormente nos issues trackers dos engenhos 
  ou podem ser encontrados casos similares em buckets distintos. Um exemplo claro dos 
  buckets duplicados podem ser encontrados atraves dos testes da suite Test262,
  onde esta suite cobre as especificacoes da linguagem em arquivos distintos e que
  podem conter mensagens de erro diferentes para um mesmo warning.

  Nos separamos os buckets considerados falso positivos de acordo com

  % Ao total, foram obtidos \nofuzzAll{} warnings, sendo estes \nofuzzHighTotal{}
  % pertencentes aos buckets com prioridade HI e \nofuzzLowTotal{} da prioridade LO. 
  % Durante 3 meses, n\'os analisamos com rigor cada log gerado, sempre checando as 
  % especificacoes do EcmaScript, a fim de encontrar bugs reais nos engenhos
  % javascript que violem condições da especificacao ou apresentem discrepancias
  % entre as saidas de cada engenhos.
  % Nosso estudo revelou que dos \nofuzzHighTotal{} buckets do grupo HI, 
  % \nofuzzHighReport{} foram reportados enquanto que no grupo LO, apenas 
  % \nofuzzLowReport{} possuiam bugs reais (ratio HI $>$ LO).
}
  % A diversidade de suites de testes influenciou na busca de bugs nao descobertos
  % pelo proprio projeto do engenhos. Por exemplo, cerca de \nofuzzTC{} buckets 
  % foram encontrados usando a suite do TC-39, alem de \nofuzzMozilla{} warnings 
  % foram obtidos do repositorio da Mozilla, \nofuzzJerry{} na suite do JerryScript, 
  % \nofuzzWebKit{} sao do WebKit e \nofuzzGoogle{} para o V8 e o Duktape, 
  % os arquivos dos repositorios do TinyJS e JSI nao mostraram discrepancias entre as
  % engines.

  % A importancia tanto de utilizar fuzzing em arquivos de teste do proprio projeto,
  % quanto em projetos distintos de mesma ordem, pois neste caso engines JS 
  % devem interpretar arquivos, entao quanto mais entradas, melhores os resultados.

  % Nosso estudo revelou que dos \tableBugsNum{} bugs reportados pelo nosso time, 
  % apenas \Fix{10} nao foram fuzzados \Fix{43.4\%},
  % Apesar do engenhos do V8 e SpiderMonkey
  % serem os mais robustos em relacao aos demais, tambem 
  % foram encontrados warnings nestes engenhos, porem

%% \Fix{nao entendi muito sobre essa subsection... 
%% seria explicacao do porque utilizar o fuzzing baseado nos nosso resultados?}
%% \Igor{
%%   Os engines JS mais populares foram arduamente testados ao longo dos últimos anos, 
%%   o sistema robusto nao significa que esta livre de bugs, ao contrario,
%%   estamos testando-o com simples entradas a partir de testes de regressao 
%%   de bugs previamente encontrados, porem estas entradas poderiam servir como seeds 
%%   para novos testcases. Partindo disso, realizar fuzzer em arquivos 
%%   existentes em projetos open-sources eh uma maneira de
%%   aumentar ainda mais a eficiencia destes engines, por exemplo o Google incentiva o 
%%   uso de fuzzers no seu ecossistema\cite{oss-fuzz,honggfuzz}.

\subsection{Fuzzing}

This section reports the results obtained by fuzzing inputs with
existing tools. It is important to mention that, to avoid experimental
noise, we did not consider the \nofuzzTotalFiles{} files (\Fix{2.8\%} of the
total) reported in the previous experiment, \ie{}, we only fuzzed test
files whose output is consistent across all engines analyzed.

>>>>

%\begin{wrapfigure}[10]{r}[0pt]{0.45\textwidth}
\begin{figure}[t]
  \centering
%  \includegraphics[trim=20 350 200
%    0,clip,width=0.35\textwidth]{google-awards-workflow}
  \includegraphics[trim=0 350 0 0,clip,width=0.65\textwidth]{diff-testing-runtimes}
  \caption{\label{fig:workflow}Differential Testing infrastructure overview.}
\end{figure}

@@

\begin{table}[t]
  \centering
  \caption{\label{tab:test-suites}Test Suites. The sections of the
    table show, respectively, the TC-39 conformance test suite, suites
    from engines we analyzed, and suites from other engines.}
  \begin{tabular}{ccr}
    \toprule
    Name & Source & \# JS files \\
    \midrule
    TC-39 (Test262) & \cite{ecma262-conformance-suite} & 31,276 \\
    \midrule
    Mozilla & \cite{mozilla} & 2,633 \\
    \veight{} & \cite{v8} & 74 \\
    \jsc{} & \cite{webkit} & 1,031 \\
    \midrule    
    Duktape & \cite{duktape} & 1,195 \\ 
    JerryScript & \cite{jerryscript} & 1,950 \\
    JSI & \cite{jsi} & 98 \\
    Tiny-js & \cite{tinyjs} & 48 \\    
    % Chakra & \cite{chakracore} & 2632 \\
    \midrule
     &  & \totalTestFiles{} \\
   \bottomrule     
  \end{tabular}
\end{table}

@@

Recall that the goal of our study is to assess reliability of
\js\ engines by leveraging implementation diversity, which is
specially rich in this domain. We report results in three
parts. First, we report on the stability of the engines we analyzed
using the Test262 standard conformance test suite for
EcmaScript~\cite{ecma262-conformance-suite}. The intuition is that the
bugs we discover throughout this study would have low relevance if the
engines are too fragile. Second, we report results obtained with test
transplantation. The hypothesis is that test cases written for one
engine may reveal bugs in different engines. The rationale is that the
domain of possible inputs is too large; consequently, we expect that
test suites of a given engine cover scenarios and corner cases
uncovered by another engine. Third, we analyzed the impact of using
cross-engine differential testing to find bugs. The hypothesis is that
even black-box fuzzers can expose important bugs.

\subsection{Stability of Engines}
\label{sec:stability}

@@

\begin{table}[h]
  \centering
  \caption{\label{tab:test262}Number of failures in Test262 over
    a 7-day period.}
  \begin{tabular}{crrrrrrr}
    \toprule
           & 1 & 2 & 3 & 4 & 5 & 6 & 7 \\
    \jsc{} & - & - & - & - & - & - & - \\
    \veight{} & - & - & - & - & - & - & - \\
    \chakra{} & - & - & - & - & - & - & - \\
    \smonkey{} & - & - & - & - & - & - & - \\
    \bottomrule 
  \end{tabular}
\end{table}

\subsection{Test Transplantation}
\label{sec:transplantation}

This section reports results obtained with test
transplantation. Table~\ref{tab:cross-testing} shows the number of
failures that each engine produces on a different test suite. To sum,
we observed that \Fix{...}

\begin{table}[h]
  \centering
  \caption{\label{tab:cross-testing}Number of failures observed exchanging
  test suites.}
  \begin{tabular}{crrrr}
    \toprule
    test suite/engine & \jsc{} & \veight{} & \chakra{} & \smonkey{} \\
    \midrule
    \jsc{} & - & - & - & -  \\
    \veight{} & - & - & - & -  \\
%    \chakra{} & - & - & - & -  \\
    Mozilla & - & - & - & -  \\
    Duktape & - & - & - & -  \\
    JerryScript & - & - & - & -  \\
    JSI & - & - & - & -  \\
    Tiny-js & - & - & - & -  \\
    \bottomrule 
  \end{tabular}
\end{table}

@@

We inspected each of those failures in detail according to the
following methodology. \Fix{..elaborate..}
Figure~\ref{tab:test-transplantation-bugs} shows
results. \Fix{...elaborate...}

\begin{table*}[t]
  \vspace{-3ex}
%  \scriptsize
  \centering
  \caption{List of bug reports issued as result of test transplantation.}
  \label{tab:test-transplantation-bugs}
  \begin{tabular}{cccccccc}
    \toprule Issue\#    & Date & Fuzz & Engine  & Status  & \multicolumn{1}{c}{Url}  & Severity & Suite \\
    \midrule    
    1  & 4/18 & \crossmark & JavascriptCore  & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}} & \Fix{x} & JerryScript      \\
   2  & 4/23 & \crossmark & Chakra  & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5033}{\#5033}} & \Fix{x} & Mozilla      \\
   3  & 4/29 & \crossmark & Chakra  & \textbf{Confirmed}   &
    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5065}{\#5065}} & \Fix{x} & Mozilla \\
   \multirow{2}{*}{4}  & \multirow{2}{*}{4/29} &  \multirow{2}{*}{\crossmark} & Chakra & \textbf{Confirmed} &    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5067}{\#5067}} & \multirow{2}{*}{\Fix{x}} & \multirow{2}{*}{Mozilla}\\
                       &  &                       &
    JavascriptCore & New &    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130} } &   & \\
   5 & 5/02 & \crossmark & JavascriptCore & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}} & \Fix{x} & Mozilla \\
   6 & 5/17 & \crossmark & Chakra & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5187}{\#5187}} & \Fix{x} & \jsc{}\\
   7 & 5/21 & \crossmark & Chakra & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5203}{\#5203}} & \Fix{x} & Mozilla\\
   8 & 6/28 & \crossmark & Chakra & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5388}{\#5388}} & \Fix{x} & \jsc{}\\
   9 & 7/10 & \crossmark & Chakra & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5442}{\#5442}} & \Fix{x} & JerryScript\\
  10 & 7/18 & \crossmark & Chakra & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5478}{\#5478}} & \Fix{x} & Mozilla\\
   11 & 7/18 & \crossmark & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187777}{\#187777}} & \Fix{x} & JerryScript\\
   \bottomrule
  \end{tabular}
\end{table*}

@@

This section reports the results obtained by fuzzing inputs, running
those inputs on different engines, and checking the outcomes with a
differential oracle (see Figure~\ref{fig:workflow}).

\subsubsection{Methodology}
In the following, we describe the methodology we used to assess the
impact of cross-engine differential testing in finding bugs on \js{}
engines. To avoid experimental noise, we did \emph{not} fuzz test
files that failed in some engine as per results reported in
Sections~\ref{sec:stability} and~\ref{sec:transplantation}. The
intuition is that we want to make sure that the bug was not
coincidental, \ie{}, the scenario where fuzzing produces an
fault-revealing input based on a test that was already
fault-revealing. That decision ensures that we can establish
cause-effect relationship between fuzzing and the observation of
discrepancy. For that reason, we discarded a total of \Fix{???} test
files from a total of \totalTestFiles{}.Recall that our tool outputs a
set of buckets, that each bucket includes a set of warnings, that each
warning is related to one file, and that a bucket is of ``lo'' or
``hi'' importance, according to the heuristic we
defined. Figure~\ref{fig:distribution} shows the distribution of
number of warnings reported per bucket. We use the names of the
fuzzing tools to refer to the results obtained with those tools. We
inspected each and every bucket for bugs, but observe that the number
of files per bucket is very high in some cases. As such, it would be
impractical to manually inspect all the files in the bucket. For that
reason, we only inspected one file per bucket. For the cases we found
the warning suspicious, we analyzed the parts of the documentation
related to the problem and, if still suspicious, we looked on the bug
tracker of the affected engine for potential duplicates. If none was
reported, we filed a bug report including the test input that
manifested the potential problem and explaining the reasons we were
suspicious. In some cases, we used the Mozila lithium
tool~\cite{lithium} to minimize the test case. For the cases of false
positives, we identified the source of false positive and moved to the
next bucket.

\subsubsection{Results}
Table~\ref{tab:summary-of-results} summarizes our results. It shows,
for each fuzzer and kind of bucket (\ie{}, hi or lo), the total number
of files involved, the number of buckets reported by our
infrastructure, the number of those that we classified as
bug-revealing (positive), and the number of those that we filed a bug
report. The difference between the last two columns corresponds to the
number of duplicates, \ie{}, the cases of bugs already reported in the
corresponding issue tracker. As expected, the hit ratio for the ``hi''
group is higher, indicating that chances of filing a bug report for a
``hi'' warning is higher.

\begin{table}[h]
  \centering
  \caption{\label{tab:summary-of-results}Summary of results.}
  \begin{tabular}{ccrrrr}
    \toprule
    \multirow{2}{*}{mode} & \multirow{2}{*}{type} & \multirow{2}{*}{\# files} &  \multicolumn{3}{c}{buckets} \\
    \cline{4-6}    
    & & & \multicolumn{1}{c}{\#} & \multicolumn{1}{c}{\# pos.} &
    \multicolumn{1}{c}{\# pos. filed} \\
    \midrule
    %% \multirow{2}{*}{nofuzz} & lo & \nofuzzFilesLO{} &  \nofuzzLOTotal{} & \Fix{.} & 11 (34) \\
    %% & hi & \nofuzzFilesHI{} & \nofuzzHITotal{} & \Fix{.} & \Fix{108 (-)} \\
    \multirow{2}{*}{\radamsa} & lo & \Fix{.} & \Fix{.} & \Fix{.} & \Fix{.} \\
    & hi & \Fix{.} & \Fix{.} & \Fix{.} & \Fix{.} \\
    \multirow{2}{*}{\quickfuzz} & lo & \Fix{.} & \Fix{.} & \Fix{.} & \Fix{.} \\
                             & hi & \Fix{.} & \Fix{.} & \Fix{.} & \Fix{.} \\    
    \bottomrule     
  \end{tabular}
\end{table}

Table~\ref{tab:false-positives} shows the distribution of false
positives per source. A false positive is a bucket that did not lend
itself in a bug report. We identified five sources of imprecision. The
source ``not yet implemented'' indicates that the engine does not
implement some part of the specification. For example, at the time of
writing, Chakra does not implement various properties from the
\CodeIn{Symbol} object. The source ``invalid input'' indicates that
the test violated some part of the specification. For example, the
test indirectly invoked some function with unexpected
arguments\Fix{provide concrete example}. In all cases that we
analyzed, that happened because fuzzing produced an invalid test
input. The source ``timeout/ome''\footnote{ome is for out of memory
  error.} indicates that the test times out (we used a 3s time budget)
or runs out of memory. That happens because engines implement
different optimizations. For example, we found that only \jsc{}
implements tail-call optimization to avoid tail
recursion. Consequently, for a certain input, \jsc{} finishes
execution quickly whereas other engines time out. The source
``implementation-dependent'' is as defined in
Section~\ref{sec:imp-dep-behavior}.\Fix{provide concrete example} The
source ``future feature'' corresponds to the case where a feature will
be part of the spec but some engines already implemented it, making a
test that uses the feature to pass only in those engines.

@@
